\newpage
\section{References}

\vspace{5mm}

\begin{itemize}[noitemsep]
    \item Should we relocate the Ports of Auckland? (2017, March 29). Retrieved from \\https://www.greaterauckland.org.nz/2015/03/26/should-we-relocate-the-ports-of-auckland/
    \item A., Liang. (2010, May). Ports of Whangarei. Retrieved from \\http://www.wdc.govt.nz/PlansPoliciesandBylaws/Plans/SustainableFutures/Documents/Sustainable \\Infrastructure/30-50-Por t-of-Whangarei.pdf
    \item Port Information Manual. (n.d.). Retrieved from \\http://northport.co.nz/Download/2007\_port\_info.pdf
    \item More talks needed on Auckland port study: Northport. (2016, July 8). Retrieved from \\http://northport.co.nz/sites/default/files/NP040\_0.pdf
    \item Frequently Asked Questions. (2018, May 11). Retrieved from \\http://www.port-tauranga.co.nz/education-2/frequently-asked-questions/
    \item Port of Tauranga Facilities. (2018, May 11). Retrieved from \\http://www.port-tauranga.co.nz/services-facilities/
    \item Berth Information. (2018, May 11). Retrieved from \\http://www.port-tauranga.co.nz/services-facilities/berth-information/
    \item POAL - Ports of Auckland Interim Results. (n.d.). Retrieved from \\http://www.poal.co.nz/media/ports-of-auckland-interim-results1
    \item Edmunds, S. (n.d.). Moving the port not as easy as redirecting ships. \\Retrieved from https://www.stuff.co.nz/business/97395638/moving-the-port-not-as-easy-as-
    \\redirecting-ships
    \item Harris, C. (n.d.). Freight expert says shifting Auckland's port northwards would hit people in pocket. \\Retrieved from https://www.stuff.co.nz/business/industries/96301195/cars-and-building-materials-\\boost-ports-of-auckland-revenue
    \item Northland Rail. (2018, March 15). Retrieved from \\https://www.greaterauckland.org.nz/2017/11/29/northland-rail-2/
    \item K. (n.d.). Developing land near rail. Retrieved from http://www.kiwirail.co.nz/developing-land-near-rail
    \item D. (n.d.). Auckland Port and the Unitary Plan. Retrieved \\from www.marketeconomics.co.nz/LiteratureRetrieve.aspx?ID=197170
    \item News and Media - Port of Tauranga Homepage. (2018, \\May 11). Retrieved from http://www.port-tauranga.co.nz/news-and-media/
    \item http://ljournal.ru/wp-content/uploads/2017/03/a-2017-023.pdf. (2017). doi:10.18411/a-2017-023
    \item Marsden Point. (n.d.). Retrieved from http://www.marsdenpoint.nz/
    \item Imports and exports. (n.d.). Retrieved from http://archive.stats.govt.nz/browse\_for\_stats/industry\_s\\ectors/imports\_and\_exports.aspx


\end{itemize}

\clearpage